\section*{Literaturverzeichnis}

\begin{thebibliography}{99}

\bibitem{Bengio-et-al-2015-Book}
Yoshua Bengio, Ian~J. Goodfellow, and Aaron Courville.
\newblock Deep learning.
\newblock Book in preparation for MIT Press
  (\url{http://www.iro.umontreal.ca/~bengioy/dlbook)}, 2015.

\bibitem{Boyd:2004:CO:993483}
Stephen Boyd and Lieven Vandenberghe.
\newblock {\em Convex Optimization}.
\newblock Cambridge University Press, New York, NY, USA, 2004.

\bibitem{Grant06disciplinedconvex}
Michael Grant, Stephen Boyd, and Yinyu Ye.
\newblock Disciplined convex programming.
\newblock In {\em Global Optimization: From Theory to Implementation, Nonconvex
  Optimization and Its Application Series}, pages 155--210. Springer, 2006.

\bibitem{NIPS2012_4824}
Alex Krizhevsky, Ilya Sutskever, and Geoffrey~E. Hinton.
\newblock Imagenet classification with deep convolutional neural networks.
\newblock In F.~Pereira, C.J.C. Burges, L.~Bottou, and K.Q. Weinberger,
  editors, {\em Advances in Neural Information Processing Systems 25}, pages
  1097--1105. Curran Associates, Inc., 2012.

\bibitem{LectureA}
Andrew Ng.
\newblock {\em Machine Learning}.
\newblock Stanford University and Coursera
  (\url{http://www.coursera.org/course/ml}).

\bibitem{nielsen}
Michael Nielsen.
\newblock {\em Neural Networks and Deep Learning}.
\newblock \url{http://neuralnetworksanddeeplearning.com/}, 2014.

\bibitem{heavyball}
Ben Recht.
\newblock {\em Optimization}.
\newblock University of Wisconsin-Madison
  (\url{http://pages.cs.wisc.edu/~brecht/cs726docs/HeavyBallLinear.pdf}).

\bibitem{strang09}
Gilbert Strang.
\newblock {\em Introduction to Linear Algebra}.
\newblock Wellesley-Cambridge Press, Wellesley, MA, 2009.

\bibitem{Moritz_Yang15}
Philipp~Moritz und Fanny~Yang.
\newblock A gentle introduction of mathematical machine learning.
\newblock Unpublished lecture notes for summer course "Learning from data", 8
  2015.

\end{thebibliography}


%\nocite{*} % alle referenzen anzeigen, sogar wenn sie nicht im text zitiert sind
%\bibliography{lit}{}
%\bibliographystyle{plain}
